Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
Added more margin comments

\begin{remark}
 As will be proven below [REF], this notation extends to an equivalence of categories from the category~$\tc$ of projective objects in~$\cat$ to the category~$\susp\tc$ of injective objects in~$\cat$.
\end{remark}

>>>>

\begin{remark}
 As will be proven below [REF]\pg{REF}, this notation extends to an equivalence of categories from the category~$\tc$ of projective objects in~$\cat$ to the category~$\susp\tc$ of injective objects in~$\cat$.
\end{remark}
